% Bibliografía manual (compatible con tectonic). Para la versión APA oficial con
% biblatex+biber, ver la nota en settings.tex y usar thesisRefs.bib.
\begin{thebibliography}{99}
\addcontentsline{toc}{chapter}{Referencias}

\bibitem{polymarket_prices}
Polymarket. (2026). \textit{Prices \& Orderbooks} [Documentación].
\url{https://docs.polymarket.com/polymarket-learn/trading/using-the-orderbook}
(Recuperado el 14 de junio de 2026).

\bibitem{polymarket_trading}
Polymarket. (2026). \textit{Order Lifecycle} [Documentación].
\url{https://docs.polymarket.com/concepts/order-lifecycle}
(Recuperado el 14 de junio de 2026).

\bibitem{wolfers2004prediction}
Wolfers, J., \& Zitzewitz, E. (2004). Prediction Markets.
\textit{Journal of Economic Perspectives, 18}(2), 107--126.

\bibitem{zhang2019deeplob}
Zhang, Z., Zohren, S., \& Roberts, S. (2019). DeepLOB: Deep Convolutional Neural
Networks for Limit Order Books. \textit{IEEE Transactions on Signal Processing,
67}(11), 3001--3012.

\bibitem{ntakaris2018}
Ntakaris, A., Magris, M., Kanniainen, J., Gabbouj, M., \& Iosifidis, A. (2018).
Benchmark dataset for mid-price forecasting of limit order book data with machine
learning methods. \textit{Journal of Forecasting, 37}(8), 852--866.

\bibitem{tsantekidis2017}
Tsantekidis, A., Passalis, N., Tefas, A., Kanniainen, J., Gabbouj, M., \& Iosifidis, A.
(2017). Using deep learning to detect price change indications in financial markets.
\textit{European Signal Processing Conference (EUSIPCO)}.

\bibitem{sirignano2019universal}
Sirignano, J., \& Cont, R. (2019). Universal features of price formation in financial
markets: perspectives from deep learning. \textit{Quantitative Finance, 19}(9), 1449--1459.

\bibitem{jha2020digital}
Jha, R., et al. (2020). Deep Learning for Digital Asset Limit Order Books.
\textit{arXiv:2010.01241}.

\bibitem{kearns2013}
Kearns, M., \& Nevmyvaka, Y. (2013). Machine Learning for Market Microstructure and
High Frequency Trading. In \textit{High Frequency Trading: New Realities for Traders,
Markets and Regulators}.

\bibitem{gu2020empirical}
Gu, S., Kelly, B., \& Xiu, D. (2020). Empirical Asset Pricing via Machine Learning.
\textit{The Review of Financial Studies, 33}(5), 2223--2273.

\bibitem{lopezdeprado2018}
López de Prado, M. (2018). \textit{Advances in Financial Machine Learning}. Wiley.

\bibitem{bailey2014deflated}
Bailey, D. H., \& López de Prado, M. (2014). The Deflated Sharpe Ratio: Correcting for
Selection Bias, Backtest Overfitting, and Non-Normality. \textit{The Journal of
Portfolio Management, 40}(5), 94--107.

\bibitem{sun2016coral}
Sun, B., Feng, J., \& Saenko, K. (2016). Return of Frustratingly Easy Domain Adaptation.
\textit{AAAI Conference on Artificial Intelligence}.

\bibitem{lim2021tft}
Lim, B., Arik, S. O., Loeff, N., \& Pfister, T. (2021). Temporal Fusion Transformers for
Interpretable Multi-horizon Time Series Forecasting. \textit{International Journal of
Forecasting, 37}(4), 1748--1764.

\bibitem{sculley2015debt}
Sculley, D., et al. (2015). Hidden Technical Debt in Machine Learning Systems.
\textit{Advances in Neural Information Processing Systems (NeurIPS)}.

\bibitem{dubach2026anatomy}
Dubach, P. D. (2026). The Anatomy of a Decentralized Prediction Market:
Microstructure Evidence from the Polymarket Order Book. \textit{arXiv:2604.24366}.

\bibitem{tsang2026election}
Tsang, K. P., \& Yang, Z. (2026). The Anatomy of a Blockchain Prediction Market:
Polymarket in the 2024 U.S. Presidential Election. \textit{arXiv:2603.03136}.

\bibitem{cheng2026arbitrage}
Cheng, G., Yang, J., \& Zou, H. (2026). Arbitrage Analysis in Polymarket NBA Markets.
\textit{arXiv:2605.00864}.

\bibitem{nechepurenko2026nonretail}
Nechepurenko, M. (2026). Fill-Side Non-Retail Trading on Polymarket: An Empirical
Study of Behavioral Tiers and Microstructure Signatures Under Quote-Attribution
Constraints. \textit{arXiv:2605.11640}.

\bibitem{qin2026polymarketv1}
Qin, B., \& Yang, R. (2026). Polymarket-v1 Database. \textit{arXiv:2606.04217}.

\bibitem{berti2025tlob}
Berti, L., \& Kasneci, G. (2025). TLOB: A Novel Transformer Model with Dual Attention
for Price Trend Prediction with Limit Order Book Data. \textit{arXiv:2502.15757}.

\bibitem{goswami2024moment}
Goswami, M., Szafer, K., Choudhry, A., Cai, Y., Li, S., \& Dubrawski, A. (2024).
MOMENT: A Family of Open Time-series Foundation Models. \textit{International
Conference on Machine Learning (ICML)}.

\bibitem{ansari2024chronos}
Ansari, A. F., et al. (2024). Chronos: Learning the Language of Time Series.
\textit{Transactions on Machine Learning Research}.

\bibitem{das2024timesfm}
Das, A., Kong, W., Sen, R., \& Zhou, Y. (2024). A Decoder-only Foundation Model for
Time-series Forecasting. \textit{International Conference on Machine Learning (ICML)}.

\bibitem{liu2025moirai2}
Liu, C., Aksu, T., Liu, J., Liu, X., Yan, H., Pham, Q., Savarese, S., Sahoo, D.,
Xiong, C., \& Li, J. (2025). Moirai 2.0: When Less Is More for Time Series
Forecasting. \textit{arXiv:2511.11698}.

\bibitem{hollmann2025tabpfn}
Hollmann, N., Müller, S., Purucker, L., Krishnakumar, A., Körfer, M., Hoo, S. B.,
Schirrmeister, R. T., \& Hutter, F. (2025). Accurate predictions on small data with
a tabular foundation model. \textit{Nature, 637}, 319--326.

\bibitem{dong2023simmtm}
Dong, J., Wu, H., Zhang, H., Zhang, L., Wang, J., \& Long, M. (2023). SimMTM:
A Simple Pre-Training Framework for Masked Time-Series Modeling. \textit{Advances in
Neural Information Processing Systems (NeurIPS)}.

\bibitem{yue2022ts2vec}
Yue, Z., Wang, Y., Duan, J., Yang, T., Huang, C., Tong, Y., \& Xu, B. (2022). TS2Vec:
Towards Universal Representation of Time Series. \textit{AAAI Conference on
Artificial Intelligence}.

\bibitem{lee2024softclt}
Lee, S., Park, T., \& Lee, K. (2024). Soft Contrastive Learning for Time Series.
\textit{International Conference on Learning Representations (ICLR)}.

\bibitem{dong2024timesiam}
Dong, J., Wu, H., Wang, Y., Qiu, Y., Zhang, L., Wang, J., \& Long, M. (2024).
TimeSiam: A Pre-Training Framework for Siamese Time-Series Modeling.
\textit{International Conference on Machine Learning (ICML)}.

\bibitem{wang2025timedart}
Wang, D., Cheng, M., Liu, Z., \& Liu, Q. (2025). TimeDART: A Diffusion Autoregressive
Transformer for Self-Supervised Time Series Representation. \textit{International
Conference on Machine Learning (ICML)}.

\bibitem{harvey2016cross}
Harvey, C. R., Liu, Y., \& Zhu, H. (2016). ...and the Cross-Section of Expected
Returns. \textit{The Review of Financial Studies, 29}(1), 5--68.

\bibitem{nosek2018preregistration}
Nosek, B. A., Ebersole, C. R., DeHaven, A. C., \& Mellor, D. T. (2018). The
preregistration revolution. \textit{Proceedings of the National Academy of Sciences,
115}(11), 2600--2606.

\bibitem{opentimestamps}
Todd, P. (2016). \textit{OpenTimestamps: Scalable, Trust-Minimized, Distributed
Timestamping with Bitcoin} [Documentación]. \url{https://opentimestamps.org}
(Recuperado el 13 de julio de 2026).

\bibitem{coletta2022worldagent}
Coletta, A., Moulin, A., Vyetrenko, S., \& Balch, T. (2022). Learning to Simulate
Realistic Limit Order Book Markets from Data as a World Agent. \textit{3rd ACM
International Conference on AI in Finance (ICAIF)}. \textit{arXiv:2210.09897}.

\bibitem{nagy2023generative}
Nagy, P., Frey, S., Sapora, S., Li, K., Calinescu, A., Zohren, S., \& Foerster, J.
(2023). Generative AI for End-to-End Limit Order Book Modelling: A Token-Level
Autoregressive Generative Model of Message Flow Using a Deep State Space Network.
\textit{arXiv:2309.00638}.

\bibitem{backhouse2025diffusion}
Backhouse, A., Li, K., Foerster, J., Calinescu, A., \& Zohren, S. (2025). Painting the
Market: Generative Diffusion Models for Financial Limit Order Book Simulation and
Forecasting. \textit{arXiv:2509.05107}.

\bibitem{jain2024lobreview}
Jain, K., Firoozye, N., Kochems, J., \& Treleaven, P. (2024). Limit Order Book
Simulations: A Review. \textit{arXiv:2402.17359}.

\end{thebibliography}
